Experiment 2

### 2021-11-12 experiments/experiment old/experiment 2.Rmd

CBtraits <- var_expt$pars[[num_div_treatment_levels]]$CB
P <- 1 #10^seq(-5, 5, 0.1)
SR <- 10^seq(0, 3, 0.1)
gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
gr_rateCB9 <- growth1(P, CBtraits$g_max_CB[num_CB_strains], CBtraits$k_CB_P[num_CB_strains]) * inhibition(SR, CBtraits$h_SR_CB[num_CB_strains])

CB_TO1 <- ggplot() +
  geom_point(aes(x = CBtraits$h_SR_CB, y = CBtraits$g_max_CB))
CB_TO2 <- ggplot() +
  geom_line(aes( x = log10(SR), y = gr_rateCB1)) +
  geom_line(aes( x = log10(SR), y = gr_rateCB9), col = "blue")

SBtraits <- var_expt$pars[[num_div_treatment_levels]]$SB
P <- 1 #10^seq(-5, 5, 0.1)
SO <- 1
O <- 10^seq(-2.5, 2.5, 0.1)
gr_rateSB1 <- growth2(P, SO, SBtraits$g_max_SB[1], SBtraits$k_SB_P[1], SBtraits$k_SB_SO[1]) *
  inhibition(O, SBtraits$h_O_SB[1])
gr_rateSB9 <- growth2(P, SO, SBtraits$g_max_SB[9], SBtraits$k_SB_P[9], SBtraits$k_SB_SO[9]) *
  inhibition(O, SBtraits$h_O_SB[9])

SB_TO1 <- ggplot() +
  geom_point(aes(x = SBtraits$h_O_SB, y = SBtraits$g_max_SB))
SB_TO2 <- ggplot() +
  geom_line(aes( x = log10(O), y = gr_rateSB1)) +
  geom_line(aes( x = log10(O), y = gr_rateSB9), col = "blue")

PBtraits <- var_expt$pars[[num_div_treatment_levels]]$PB
P <- 1 #10^seq(-5, 5, 0.1)
SO <- 1
O <- 10^seq(-2.5, 2.5, 0.1)
gr_ratePB1 <- growth2(P, SO, PBtraits$g_max_PB[1], PBtraits$k_PB_P[1], PBtraits$k_PB_SR[1]) *
  inhibition(O, PBtraits$h_O_PB[1])
gr_ratePB9 <- growth2(P, SO, PBtraits$g_max_PB[9], PBtraits$k_PB_P[9], PBtraits$k_PB_SR[9]) *
  inhibition(O, PBtraits$h_O_PB[9])

PB_TO1 <- ggplot() +
  geom_point(aes(x = PBtraits$h_O_PB, y = PBtraits$g_max_PB))
PB_TO2 <- ggplot() +
  geom_line(aes( x = log10(O), y = gr_ratePB1)) +
  geom_line(aes( x = log10(O), y = gr_ratePB9), col = "blue")

(CB_TO1 + SB_TO1 + PB_TO1) / (CB_TO2 + SB_TO2 + PB_TO2)
```

>>>>

```{r}
display_diversity(
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```
